SMT-Based Generation of Symbolic Automata \thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-11-20 2017-Xudong-SMT/ActaInformatica.tex
typos

In \cite{henrio:Forte2016} we also proved the following result, which
ensures the termination of our semantic construction algorithm.
Note that this theorem and its proof were part of previous versions of this work, when Algorithm 1 did not include the fixpoint Refinement computation. Proof of termination of the fixpoint itself will be discussed as part of the proof of Theorem \ref{Th:CorrectnessWithAssignments}.

>>>>

In \cite{henrio:Forte2016} we also proved the following result, which
ensures the termination of our semantic construction algorithm.
Note that this theorem and its proof were part of previous versions of this work, when Algorithm 1 did not include the fixed point refinement computation. Proof of termination of the fixed point itself will be discussed as part of the proof of Theorem \ref{Th:CorrectnessWithAssignments}.
